Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-01-09 images/text/mdag_bb2.tex
section:appendix; process:write

    % dag_bb3
    \node at (-2,0) {$e_{X}$};
    \node at (-1,0) {$X$};
    \node at (-1,-1.1) {$e_{Z}$};
    \node at (0,-1.1) {$Z$};
    \node at (1,0) {$Y$};
    \node at (2,0) {$e_{Y}$};

    \draw[{Circle[open]}-{latex}](-2,-0.3) to (-1,-0.3); % eX -> X (circle)
    \draw[{Circle}-{latex}](-1,-0.27) to (0,-0.85); % X -> Z
    \draw[{Circle[open]}-{latex}](-1,-0.88) to (0,-0.88); % eZ -> Z (circle)
    \draw[{Circle}-{latex}{Circle}](1,-0.27) to (0,-0.9); % Z -> Y
    \draw[{Circle[open]}-{latex}](2,-0.3) to (1,-0.3); % eY -> Y (circle)

>>>>

    % dag_bb2
    \node at (-2,0) {$e_{X}$};
    \node at (-1,0) {$X$};
    \node at (0,0) {$Y$};
    \node at (1,0) {$e_{Y}$};

    \draw[{Circle[open]}-{latex}](-2,-0.3) to (-1.05,-0.3); % eX -> X (circle)
    \draw[{Circle[open]}-{latex}](1,-0.3) to (0.05,-0.3); % eY -> Y (circle)
    \draw[{Circle}-{latex}{Circle}](-1.05,-0.3) to (0.05,-0.3); % X -> Y (circle)
